\section{Work Experience}
  \CVSubHeadingListStart
    % \CVSubheading
    %   {Research Intern}{Winter 2020 -- Present}
    %   {University of Wisconsin - Madison}{Madison, WI}
    % %   \CVItemListStart
    % %     \CVItem{}
    % %     \CVItem{}
    % %   \CVItemListEnd

    % \CVSubheading
    %   {Co-Founder}{Fall 2023 -- Present}
    %   {PocketEngineer LLC}{}
    %   \CVItemListStart
    %     \CVItem{Developed an automated system that crawls and stores a company's product spec sheets and tech manuals.}
    %     \CVItem{Built system to transcribe sales calls and generate LLM RAG-based product suggestions and product Q\&A in real time.}
    %   \CVItemListEnd

    \CVSubheading
      {Graduate Research Assistant}{Fall 2021 -- Present}
      {University of Michigan}{}
      \CVItemListStart
        \CVItem{Creating automated data collection and annotation methods for training vision-language models to achieve above-human performance on in-the-wild text recognition tasks ($>$10k samples).~\cite{hawkeye}}
        \CVItem{Designed a real-time software privacy film for smartphones, Eye-Shield. Reduced attack rates to 24.24\% for images and 15.91\% for text, protecting against screen snooping on smartphones.~\cite{ShoulderSurfing}}
        \CVItem{Developed various LLM web automation tools and document parsers for auditing data collection activities~\cite{steward}. Deployed automated analysis of 47.2k Chrome Web Store extensions~\cite{BrowserExtensions}, 2.9k online trackers~\cite{OptOutChk}, and 1.4k cookie banners~\cite{ConsentChk}, finding many instances of misleading disclosures and non-compliance.}
        \CVItem{Built and evaluated an LLM chatbot engine using GPT-4o and GPT-3.5 for serving personalized advertisements. Ran a user study with 179 participants, finding users were 13.07\% more influenced by the LLM serving ads compared to the control. Undisclosed advertising led to 19.05\% more positive reactions to products.~\cite{chatbotads}}
        \CVItem{Served as server admin, social organizer, equipment curator, and mentoring role for the Real-Time Computing Lab.}
      \CVItemListEnd

    \CVSubheading
      {Undergraduate Research Assistant}{Fall 2018 -- Spring 2021}
      {University of Wisconsin - Madison}{}
      \CVItemListStart
        \CVItem{Researched fairness properties of face recognition systems.~\cite{Fairness}}
        \CVItem{Created a controller for social robots to preserve conversational privacy.~\cite{HRIPrivacy}}
        \CVItem{Explored using physical invariants from LiDAR to improve ML classifier robustness against adversarial attacks.~\cite{Robustness}}
        \CVItem{Developed an anti face recognition system using adversarial attacks to protect online photo privacy.~\cite{FaceOff}}
        \CVItemListEnd

    \CVSubheading
      {Software Engineering Intern}{Summer 2019}
      {Roblox Corporation}{}
      \CVItemListStart
        \CVItem{Designed and implemented production autocomplete, smart-cursor movement, and suggestion features for Roblox Studio’s script editor using TDD. Integrated 30 JavaScript Squish tests to auto-validate UI behavior and prevent errors.}
      \CVItemListEnd

    \CVSubheading
      {Software Engineering Intern}{Summer 2018}
      {Optum, UnitedHealth Group}{}
      \CVItemListStart
        \CVItem{Designed and implemented an attack-surface visualization that aggregated and normalized 50M+ vulnerability and asset records, produced correlated risk scores, and an interactive dashboard. Presented results to Optum's leadership.}
    \CVItemListEnd

  \CVSubHeadingListEnd